\documentclass{article}
\linespread{1.3}
\usepackage[margin=50pt]{geometry}
\usepackage{amsmath, amsthm, amssymb, amsthm, tikz, fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\changefont}{\fontsize{15}{15}\selectfont}

\fancypagestyle{firstpageheader}
{
  \fancyhead[R]{\changefont Michael Huang \\ Homework 7 \\ Adekoya}
}

\begin{document}

\thispagestyle{firstpageheader}

\section*{1.}
{\Large 

The time (in hours) required to repair a machine is an exponentially distributed r.v. with
parameter $\lambda = 1$.

\subsection*{(a)}
What is the probability that a repair time exceeds 1 hour?


\subsection*{(b)}
What is the conditional probability that a repair takes at least 10 hours, given that its duration
exceeds 9 hours?


}

\section*{2.}
{\Large

David is deciding to buy either a new car or a used car that has been driven 10,000 miles. For
each car, find the probability that he can drive it for an extra 20,000 miles in the following
scenarios.

\subsection*{(a)}
The total mileage that both cars can be driven before they completely break down is an
exponential random variable with mean 20 thousand miles.


\subsection*{(b)}
he total mileage that both cars can be driven before they completely break down is
uniformly distributed over (0, 40,000).


}

\section*{3.}
{\Large 

Let  $X, Y$ be continuous r.v.s with the following joint probability density function:

\[
f_{X,Y}\left(x,y\right)=\begin{cases}
e^{-x}\cdot\frac{k}{\sqrt{x}}& \,0< x,\,\, 0\le|y| \le \sqrt{x};\\
0 & \,\mbox{otherwise,}
\end{cases}
\]

\subsection*{(a)}
Find the constant k.


\subsection*{(b)}
Find the marginal density $f_X (x)$ and identify the distribution of $X$.


}

\section*{4.}
{\Large 
The random vector $(X, Y)$ is said to be uniformly distributed over a region $R$ if, for some
constant $c$, its joint density is

\[
f_{X,Y}\left(x,y\right)=\begin{cases}
c& \,\mbox{if} \left(x,y\right)\in\mathbb R\\
0 & \,\mbox{otherwise,}
\end{cases}
\]

\subsection*{(a)}
Show that $\frac{1}{c}=$  area of region $R$.


\subsection*{(b)}
Suppose $(X, Y)$  is uniformly distributed over the square centered at (0, 0) and with sides
of length 2. Show that $X$ and $Y$ are independent, with each being distributed uniformly
over $(-1,1)$


\subsection*{(c)}
What is the probability that $(X, Y)$ lies in the circle of radius 1 centered at the origin?
That is, find $\mathrm P \,(X^2 + Y^ 2 \le 1)$.


}

\section*{5.}
{\Large 
The time that it takes to service a car is an exponential random variable with rate 1.

\subsection*{(a)}
If A. J. brings his car in at time 0 and M. J. brings her car in at time t, what is the
probability that M. J.’s car is ready before A. J.’s car? (Assume that service times are
independent and service begins upon arrival of the car.)


\subsection*{(b)}
If both cars are brought in at time 0, with work starting on M. J.’s car only when A.J.’s
car has been completely serviced, what is the probability that M. J.’s car is ready before
time 2?


}

\section*{6.}
{\Large 
Suppose  $X, Y$  are independent random variables with probability density functions
\[f_X (t) = f_Y (t) =\frac12e^{-|t|}, \,\,\, t \in \mathbb R\]
Find the pdf $f_Z (t)$ of $Z = X + Y$ . Hint: Consider the cases $t < 0$ and $t \ge 0$ separately.


}

\end{document}